Running Anpan

### 2023-03-31 other/anpan.qmd
sdd some other bugs

>>>>

```{r}
bwex_results <- anpan(#bug_dir           = "/grace/sequencing/processed/mgx/humann/main",
                        bug_file          = "./data/anpan/Blautia_wexlerae_pathabundance.tsv",
                        meta_file         = "./data/anpan/manuscript_meta.csv",
                        out_dir           = "./data/anpan/Blautia_wexlerae",
                        # annotation_file   = "/path/to/annotation.tsv", #optional, used for plots
                        filtering_method  = "kmeans",
                        model_type        = "fastglm",
                        covariates        = c("sex", "education"),
                        outcome           = "ageMonths",
                        plot_ext          = "pdf",
                        save_filter_stats = TRUE)

input_path = file.path("data", "anpan", "Blautia_wexlerae", "filter_stats",
                       "filtered_Blautia_wexlerae_pathabundance.tsv.gz")

plot_results(res         = bwex_results,
             model_input = model_input,
             covariates        = c("sex", "education"),
            outcome           = "ageMonths",
             bug_name    = "Blautia wexlerae",
             cluster     = "both",
             show_trees  = TRUE)
